\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of G dwarfs

### 2017-06-21 paper/ms.tex
working

\usepackage{setspace}
\onehalfspacing
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb}
\usepackage[sort&compress,super]{natbib}
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage{aas_macros}
\usepackage{hyperref}
\hypersetup{backref,breaklinks,colorlinks,citecolor=blue}
\usepackage{mathptmx}

@@

% ------------------------
% nature summary paragraph
% ------------------------
% - a fully referenced paragraph, ideally of about 200 words, but certainly no
%   more than 300 words, aimed at readers in other disciplines.
% - This paragraph starts with a 2-3 sentence basic introduction to the field;
%   followed by a one-sentence statement of the main conclusions starting 'Here
%   we show' or equivalent phrase; and finally, 2-3 sentences putting the main
%   findings into general context so it is clear how the results described in
%   the paper have moved the field forwards.
% - annotated example: https://www.nature.com/nature/authors/gta/2c_Summary_para.pdf
% ------------------------
\section{Summary}
{\bf \noindent
  Stars that are born together are expected to have same chemical compositions initially.
  Detailed chemical abundance studies of stars in wide binaries indeed reveal nearly identical
  chemistry in most cases\citep{Gratton:2001aa,Desidera:2004aa} as well as stars in open clusters\cite{Bovy:2016aa}.
  However, formation and evolution of different planetary systems around each star in a wide binary
  may eventually lead to a difference in compositions of the component stars' radiative and
  convective layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
  Wide binary systems of two twin-like stars are particularly useful
  as they are not subject to confusion with Galactic chemical evolution.
  A handful of wide binaries that show small differences in their surface
  chemical abundances have been reported so far
  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}.
  However, a convincing example is yet to be found.
  Here we report a comoving pair of bright sun-like stars, HD~240430 and HD~240429,
  with a significant difference ($\approx 0.2$~dex) in their chemical
  abundances that strongly suggests accretion of rocky planetary system in one
  of the stars within the last couple of billion years.
  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as large
  an enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
  The two stars also show high Li abundance given their age of $\sim 4$ Gyr
  inferred from their stellar parameters.
  A prominent trend of element abundance enhancement with condensation temperature
  indicates the accreted material is rocky.
  We therefore suggest that the star HD~240430, ``Kronos'', recently accreted
  $\approx 20$~\mearth\ of rocky material after birth selectively enhancing the
  refractory elements in its surface and convective envelope.
  The other star HD~240429, ``Krios'', may also have had a similar accretion
  event given its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  This pair of stars provides evidence that dynamical accretion of rocky planets
  happen during the lifetime of sun like stars.
}

@@

\begin{table*}[htpb]
  \caption{Astrometric and spectroscopic measurements.}
  \label{tab:t1}
  \centering
  \begin{tabular}{ccc}
\hline\hline
Name & HD 240429 & HD 240430 \\
\hline
Sp Type                                   & G2                & G0                \\
$T_\mathrm{eff}$                          & 5878              & 5803              \\
$\log{g}$                                 & 4.43              & 4.33              \\
$v\sin{i}$                                & 1.1               & 2.5               \\
$[\elem{Fe}/\elem{H}]$                    & 0.01              & 0.20              \\
$v_r$                                     & $-21.2$           & $-21.2$           \\
$\varpi$ \footnotemark[1]                 & $9.35 \pm 0.24$   & $9.41 \pm 0.25$   \\
$\mu_\alpha^*$ \footnotemark[1]           & $89.25 \pm 0.66$  & $89.41 \pm 0.69$  \\
$\mu_\delta$ \footnotemark[1]             & $-29.68 \pm 0.54$ & $-30.12 \pm 0.52$ \\
\hline\hline 
\end{tabular}
\end{table*}

\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search for comoving stars using the proper motions and parallaxes
from the {\it Tycho-Gaia Astrometric Solution} catalog (hereafter \tgas), a
component of the first data release of the astrometric space mission \gaia\cite{2016A&A...595A...2G}
(the astrometric measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2 both similar to the Sun (G2).
In a separate effort to study detailed chemical abundances of potential
planet-hosting stars, high resolution, high signal-to-noise ratio spectra of
both stars were obtained using the HIRES spectrograph on the Keck-I
telescope\cite{2016ApJS..225...32B}. 
The spectral resolution is $R=\lambda/\Delta\lambda\approx 70000$ and the
wavelength coverage is $5164$--$7799$~\AA.
A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities.

The projected separation between the pair is 1.9 arcmin\ ($\approx 0.01$~pc),
and the 3D separation is $\approx 0.6$~pc.
Although selected based only on their astrometry, the two stars
have identical radial velocities within uncertainties (Table~\ref{tab:t1}),
confirming that they are truly comoving.
As the separation is smaller than the Jacobi radius (1.2~pc) in the solar
neighborhood for a 2~\msun\ binary system\cite{Jiang:2010aa}, \bizarreone\ and
\sunanalog\ are likely a bound wide binary system that formed coevally.

Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
We then combine the luminosities with $T_\mathrm{eff}$, \elemH{Fe}, \elemH{Si}
in order interpolate the mass, age, radius, and $\log(g)$ of each star
in a grid of Yale-Yonsei model isochrones\cite{2013ApJ...776...87S}.
The best-fit isochrone ages of \sunanalog\ and \bizarreone\ are
$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
consistent with them being coeval.

However, one of the stars, \bizarreone\, is significantly more metal
rich than the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
Moreover, not all elements are equally enhanced:
the abundances of \bizarreone\ show selective under-enhancement in
\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}
relative to \elem{Fe} and other refractory elements.
%
The validity of the measured abundance differences is further demonstrated
in \figname~\ref{fig:spec1} and \ref{fig:spec2} where we show
segments of the spectra and models of the two stars
used to measure their abundances.
As expected from their reported metallicity difference ($\Delta\feh \approx 0.2$),
the ratio of data and model between the two stars show significant
residuals of almost all metal line features, largely dominated by \elem{Fe}.
However, for lines of elements that are not as enhanced in \bizarreone\,
the residuals are much smaller in amplitude.

The observed difference in metallicity and abundances are genuinely rare and
unexpected.
None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) wide
binary pairs examined using spectra of comparable quality and the same
consistent measurement pipeline shows discrepancies in abundances between the
stars at this level\cite{2016ApJS..225...32B} (see Figure~\ref{fig:deltaXH}).
The maximum metallicity difference observed in the other pairs is $\Delta\feh = 0.03$~dex
with $1\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
This is consistent with similar studies of metallicity and abundance differences
in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
The difference of $\approx 0.2$~dex is also the largest among a handful of
wide binaries that do show metallicity and abundance differences with varying
significance\cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,
  Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
(see Figure~\ref{fig:relabun_tcrank}).

Both stars have high surface \elem{Li} abundances considering
their ages of $\sim 4$~Gyr.
The surface lithium abundance in a sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
burning.
The \elem{Li} doublet at $6707.6$~\AA, which is usually too weak to be
detectable at this age even for high signal-to-noise spectra, is clearly
visible in the spectra of both stars (see \figname~\ref{fig:spec2}).
The measured absolute abundances for \bizarreone\ and \sunanalog\ are
$2.75$~dex and $2.25$~dex, respectively (Myles \etal, in prep),
resulting in the largest abundance difference ($\approx 0.5$~dex) seen
among all measured elements.

@@

The element \elem{Li} is worth special attention in the context of the
accretion scenario.
Because Li is present in either carbonaceous chondrites or bulk Earth with
a concentration of $1-1.5$~ppm in mass (\cite{mcdonough2001composition}),
but is depleted quickly within the first couple of Gyrs on the surface of a
Sun-like star, accretion of either material at later times will significantly
replenish the lithium on the star's surface.
For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
material would result in $\Delta\elemH{Li} \approx 1.6$~dex (which
is indicated as an upward arrow in \figname~\ref{fig:toycalc}).
Incidentally, the star under examination, \bizarreone, has an age (informed by
stellar parameters) very close to the Sun ($4.28_{-1.03}^{+1.11}$~Gyr).
Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with $1.6$~dex
enhancement in its \elem{Li}.
This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \cite{jmlithium})
approximately $1.65$~dex higher than the solar value of $1.1$~dex
(\todo{needs reference}).
Furthermore, this implies that the accretion event should have happened very
recently, or at least within the \elem{Li} depletion time ($\lesssim 1$~Gyr).

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec2.pdf}
  \caption{Same as \figname~\ref{fig:spec1}
    but for smaller portions of spectra at longer wavelengths that are
    not dominated by \elem{Fe}.
    We mark elements that give rise to strong absorption lines.
    The feature in the third column of the second row is a strong \elem{Li}
    line that was not modeled by \citealt{2016ApJS..225...32B}; this line was
    studied in a separate work (\citealt{jmlithium}).
    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
    show weaker residuals.
  }
  \label{fig:spec2}
\end{figure}

@@

Combining the precise radial velocities obtained from spectra with the \tgas\
astrometry, we can compare differences between the inferred 6D phase-space
coordinates of the two stars.
We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $v_r$,
given the observed parallax, $\hat\pi$, and proper motions,
$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$.
We assume the noise is Gaussian, and the radial velocity measurement is
uncorrelated with the astrometric measurements.
If we define
\begin{eqnarray}
  \vec{\hat y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \hat\pi &
          \hat\mu_{\alpha^*} &
          \hat\mu_\delta &
          \hat v_r
        \end{array}
      \right)}\\
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          v_r
        \end{array}
      \right)}
\end{eqnarray}
then the likelihood is
\begin{equation}
  \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
\end{equation} where $\mat{C}$ is the covariance matrix.
We adopt a uniform space density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
%
For each of the two stars, we use \project{emcee}
(\citealt{2013PASP..125..306F}) to generate posterior samples in $(r, v_\alpha,
v_\delta, v_r)$ by running 64 walkers for 4608 steps and discarding the first
512 steps as the burn-in period.
For each sample, we convert the heliocentric phase-space coordinates into
Galactocentric coordinates assuming that the Sun's position and velocity are
$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
(-11.1,\,244,\,7.25)~\kms$ \citep[e.g.,][]{Schonrich:2010, Schonrich:2012}.

@@

We estimate how much mass of rocky material is needed to explain an increment of
$\approx 0.2$~dex in refractory elements.
We carry out simple toy calculations of expected $\Delta\elemH{X}$
in a Sun-like star's atmosphere by adding certain mass of bulk Earth composition
under these simplifying assumptions:
\begin{itemize}
  \item The material added is instantly and completely mixed.
  \item The atmospheric composition that we measure is identical throughout
    the star's radiative and convective zone.
  \item The surface abundance of the star has been altered only by the
    accretion event(s).
\end{itemize}
We take the solar abundances, $\elemH{X}$, of element \elem{X}
(\cite{Asplund:2009aa}) which can be converted to mass fraction as
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in e.g., atomic mass unit.
Assuming that the added material has a total mass $M_\mathrm{add}$, and the
mass fraction in each element $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
We take the composition of bulk Earth from a chondritic model of the Earth
(\cite{mcdonough2001composition}).
Similar calculations have been performed by \citet{Chambers:2010aa} and
\citet{Mack:2014aa,Mack:2016aa}.

>>>>

\usepackage{setspace}
\onehalfspacing
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb}
\usepackage[sort&compress,super]{natbib}
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage{aas_macros}
\usepackage{hyperref}
\hypersetup{backref,breaklinks,colorlinks,citecolor=blue}
\usepackage{mathptmx}
\usepackage{threeparttable}

@@

% ------------------------
% nature summary paragraph
% ------------------------
% - a fully referenced paragraph, ideally of about 200 words, but certainly no
%   more than 300 words, aimed at readers in other disciplines.
% - This paragraph starts with a 2-3 sentence basic introduction to the field;
%   followed by a one-sentence statement of the main conclusions starting 'Here
%   we show' or equivalent phrase; and finally, 2-3 sentences putting the main
%   findings into general context so it is clear how the results described in
%   the paper have moved the field forwards.
% - annotated example: https://www.nature.com/nature/authors/gta/2c_Summary_para.pdf
% ------------------------
\section{Summary}
{\bf \noindent
  Stars that are born together are expected to have same chemical compositions
  initially.
  Detailed chemical abundance studies of stars in wide binaries indeed reveal
  nearly identical chemistry in most
  cases\citep{Gratton:2001aa,Desidera:2004aa} as well as stars in open
  clusters\cite{Bovy:2016aa}.
  However, formation and evolution of different planetary systems around each
  star in a wide binary may eventually lead to a difference in compositions of
  the component stars' radiative and convective
  layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
  Wide binary systems of two twin-like stars are particularly useful
  as they are not subject to confusion with Galactic chemical evolution.
  A handful of wide binaries that show small differences in their surface
  chemical abundances have been reported so far
  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,
    Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}.
  However, a convincing example is yet to be found.
  Here we report a comoving pair of bright sun-like stars, HD~240430 and HD~240429,
  with a significant difference ($\approx 0.2$~dex) in their chemical
  abundances that strongly suggests accretion of rocky planetary system in one
  of the stars within the last couple of billion years.
  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as large
  an enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
  The two stars also show high Li abundance given their age of $\sim 4$ Gyr
  inferred from their stellar parameters.
  A prominent trend of element abundance enhancement with condensation temperature
  indicates the accreted material is rocky.
  We therefore suggest that the star HD~240430, ``Kronos'', recently accreted
  $\approx 20$~\mearth\ of rocky material after birth selectively enhancing the
  refractory elements in its surface and convective envelope.
  The other star HD~240429, ``Krios'', may also have had a similar accretion
  event given its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  This pair of stars provides evidence that dynamical accretion of rocky planets
  happen during the lifetime of sun like stars.
}

@@

\begin{table*}[htpb]
  \centering
  \begin{threeparttable}
  \caption{Astrometric and spectroscopic measurements of the pair\label{tab:t1}}
\begin{tabular}{ccccc}
\hline\hline
                        &                & \sunanalog\            & \bizarreone\           &               \\
Name                    & Units          & HD 240429              & HD 249439              & Uncertainties \\
\hline
Sp Type                 &                & G2                     & G0                     &               \\
R.A.\tnote{a}           & hh:mm:ss       & 23:51:55.21            & 23:52:09.42            &               \\
Dec.\tnote{a}           & dd:mm:ss       & 59:42:48.16            & 59:42:26.08            &               \\
2MASS $J$\tnote{a}      & mag            & $8.593 \pm 0.023$      & $8.415 \pm 0.026$      &               \\
$T_\mathrm{eff}$        & K              & 5878                   & 5803                   & 25            \\
$\log{g}$               &                & 4.43                   & 4.33                   & 0.028         \\
$v\sin{i}$              & \kms\          & 1.1                    & 2.5                    &               \\
$[\elem{Fe}/\elem{H}]$  &                & 0.01                   & 0.20                   & 0.010         \\
Age\tnote{b}            & Gyr            & $4.00_{-1.56}^{+1.51}$ & $4.28_{-1.03}^{+1.11}$ &               \\
$v_r$                   & \kms\          & $-21.2$                & $-21.2$                & 0.2           \\
$\varpi$\tnote{a}       & mas            & $9.35 \pm 0.24$        & $9.41 \pm 0.25$        &               \\
$\mu_\alpha^*$\tnote{a} & mas\,yr$^{-1}$ & $89.25 \pm 0.66$       & $89.41 \pm 0.69$       &               \\
$\mu_\delta$\tnote{a}   & mas\,yr$^{-1}$ & $-29.68 \pm 0.54$      & $-30.12 \pm 0.52$      &               \\
\hline 
\multicolumn{5}{c}{$T_c < 1200$~K} \\
\hline 
$A(\elem{Li})$\tnote{c} &                & $2.25$                 & $2.75$                 &               \\
$\elemH{C}$             &                & $0.00$                 & $0.09$                 & 0.026         \\
$\elemH{N}$             &                & $-0.06$                & $-0.01$                & 0.042         \\
$\elemH{O}$             &                & $0.01$                 & $0.09$                 & 0.036         \\
$\elemH{Na}$            &                & $-0.06$                & $-0.04$                & 0.014         \\
$\elemH{Mn}$            &                & $-0.03$                & $0.00$                 & 0.020         \\
\hline 
\multicolumn{5}{c}{$T_c > 1200$~K} \\
\hline 
$\elemH{Mg}$            &                & $0.01$                 & $0.19$                 & 0.012         \\
$\elemH{Al}$            &                & $0.01$                 & $0.21$                 & 0.028         \\
$\elemH{Si}$            &                & $0.00$                 & $0.16$                 & 0.008         \\
$\elemH{Ca}$            &                & $0.02$                 & $0.23$                 & 0.014         \\
$\elemH{Ti}$            &                & $0.02$                 & $0.20$                 & 0.012         \\
$\elemH{V}$             &                & $0.02$                 & $0.20$                 & 0.034         \\
$\elemH{Cr}$            &                & $0.01$                 & $0.17$                 & 0.014         \\
$\elemH{Fe}$            &                & $0.01$                 & $0.20$                 & 0.010         \\
$\elemH{Ni}$            &                & $-0.01$                & $0.21$                 & 0.014         \\
$\elemH{Y}$             &                & $0.04$                 & $0.26$                 & 0.030         \\

\end{tabular}
\begin{tablenotes}
\item [a] From \tgas.
\item [b] Derived in this work by isochrone fitting using the Yale-Yonsei model
  isochrones\cite{2013ApJ...776...87S}.
\item [c] Absolute abundances from Myles \etal, in prep.
\item All values are from \citet{2016ApJS..225...32B} unless otherwise noted.
\end{tablenotes}
\end{threeparttable}
\end{table*}

% general description of the pair and measurements
\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search for comoving stars using the proper motions and parallaxes
from the {\it Tycho-Gaia Astrometric Solution} catalog (hereafter \tgas), a
component of the first data release of the astrometric space mission \gaia\cite{2016A&A...595A...2G}
(the astrometric measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2 both similar to the Sun (G2).
In a separate effort to study detailed chemical abundances of potential
planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
both stars were obtained using the HIRES spectrograph on the Keck-I
telescope\cite{2016ApJS..225...32B}. 
The wavelength coverage is $5164$--$7799$~\AA.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities.

% likely origin given its proximity in phase space
% TODO reference dxdv figure here
The projected separation between the pair is 1.9 arcmin\ ($\approx 0.01$~pc),
and the 3D separation is $\approx 0.6$~pc.
Although selected based only on their astrometry, the two stars
have identical radial velocities within uncertainties (Table~\ref{tab:t1}),
confirming that they are truly comoving.
As the separation is smaller than the Jacobi radius (1.2~pc) in the solar
neighborhood for a 2~\msun\ binary system\cite{Jiang:2010aa}, \bizarreone\ and
\sunanalog\ are likely a bound wide binary system that formed coevally.

% coevality based on stellar parameters
% TODO reference supplement discussion on age here?
Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
We then combine the luminosities with $T_\mathrm{eff}$, \elemH{Fe}, \elemH{Si}
in order interpolate the mass, age, radius, and $\log(g)$ of each star
in a grid of Yale-Yonsei model isochrones\cite{2013ApJ...776...87S}.
The best-fit isochrone ages of \sunanalog\ and \bizarreone\ are
$4.00_{-1.56}^{+1.51}$~Gyr and $4.28_{-1.03}^{+1.11}$~Gyr, respectively,
consistent with them being coeval.

% metallicity and abundance difference
However, one of the stars, \bizarreone\, is significantly more metal rich than
the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
Moreover, not all elements are equally enhanced: the abundances of \bizarreone\
show selective under-enhancement in \elem{C}, \elem{N}, \elem{O}, \elem{Na},
and \elem{Mn} relative to \elem{Fe} and other refractory elements.
As expected from their measured metallicity difference, the ratio of data and
model between the two stars show significant residuals of almost all metal line
features, largely dominated by \elem{Fe}.
However, for lines of elements that are not as enhanced in \bizarreone\, the
residuals are much smaller in amplitude demonstrating the validity of the
measured abundance differences (see
Figure~\ref{fig:spec1} and \ref{fig:spec2}).

% novelty
The observed difference in metallicity and abundances are genuinely rare and
unexpected.
None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) wide
binary pairs examined using spectra of similar quality and the same
consistent measurement pipeline shows discrepancies in abundances between the
stars at this level\cite{2016ApJS..225...32B} (see Figure~\ref{fig:deltaXH}).
The maximum metallicity difference observed in the other pairs is $\Delta\feh =
0.03$~dex with $1\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
This is consistent with similar studies of metallicity and abundance
differences in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
The difference of $\approx 0.2$~dex is also the largest among a handful of wide
binaries that do show metallicity and abundance differences with varying
significance\cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,
  Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
(see Figure~\ref{fig:relabun_tcrank}).

% high Li
Both stars have high surface \elem{Li} abundances considering
their ages of $\sim 4$~Gyr.
The surface lithium abundance in a sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
burning. %TODO: REFERENCE
The \elem{Li} doublet at $6707.6$~\AA, which is usually too weak to be
detectable at this age even for high signal-to-noise spectra, is clearly
visible in the spectra of both stars (see \figname~\ref{fig:spec2}).
The measured absolute abundances for \bizarreone\ and \sunanalog\ are
$2.75$~dex and $2.25$~dex, respectively (Myles \etal, in prep),
resulting in the largest abundance difference ($\approx 0.5$~dex) seen
among all measured elements.

@@

The accretion scenario can naturally explain the anomalously high
surface \elem{Li} abundance in \bizarreone.
Because \elem{Li} is strongly depleted in old sun-like stars yet
present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
late-time accretion of rocky planetary material will significantly
replenish the lithium on the star's surface.
For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
material would result in $\Delta\elemH{Li} \approx 1.6$~dex (which
is indicated as an upward arrow in \figname~\ref{fig:toycalc}).
Incidentally, the star under examination, \bizarreone, has an age (informed by
stellar parameters) very close to the Sun ($4.28_{-1.03}^{+1.11}$~Gyr).
Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with $1.6$~dex
enhancement in its \elem{Li}.
This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \cite{jmlithium})
approximately $1.65$~dex higher than the solar value of $1.1$~dex
(\todo{needs reference}).
Furthermore, this implies that the accretion event should have happened very
recently, or at least within the \elem{Li} depletion time ($\lesssim 1$~Gyr).

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec2.pdf}
  \caption{Same as \figname~\ref{fig:spec1}
    but for smaller portions of spectra at longer wavelengths that are
    not dominated by \elem{Fe}.
    We mark elements that give rise to strong absorption lines.
    The feature in the third column of the second row is a strong \elem{Li}
    line that was studied in Myles \etal, in prep.
    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
    show noticeably weaker residuals compared to neighboring lines of
    refractory elements.
  }
  \label{fig:spec2}
\end{figure}

@@

Combining the precise radial velocities obtained from spectra with the \tgas\
astrometry, we can compare differences between the inferred 6D phase-space
coordinates of the two stars.
We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $v_r$,
given the observed parallax, $\hat\pi$, and proper motions,
$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$.
We assume the noise is Gaussian, and the radial velocity measurement is
uncorrelated with the astrometric measurements.
If we define
\begin{eqnarray}
  \vec{\hat y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \hat\pi &
          \hat\mu_{\alpha^*} &
          \hat\mu_\delta &
          \hat v_r
        \end{array}
      \right)}\\
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          v_r
        \end{array}
      \right)}
\end{eqnarray}
then the likelihood is
\begin{equation}
  \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
\end{equation} where $\mat{C}$ is the covariance matrix, and $\mathcal{N}$ is
normal (Gaussian) distribution.
We adopt a uniform space density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
%
For each of the two stars, we use \project{emcee}\cite{2013PASP..125..306F}
to generate posterior samples in $(r, v_\alpha, v_\delta, v_r)$
by running 64 walkers for 4608 steps and discarding the first
512 steps as the burn-in period.
For each sample, we convert the heliocentric phase-space coordinates into
Galactocentric coordinates assuming that the Sun's position and velocity are
$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
(-11.1,\,244,\,7.25)~\kms$\cite{Schonrich:2010, Schonrich:2012}.

@@

We estimate how much mass of rocky material is needed to explain an increment of
$\approx 0.2$~dex in refractory elements observed in \bizarreone\
relative to \sunanalog.
Because \sunanalog\ is a solar-twin star in that its $T_\mathrm{eff}$, \logg,
and \feh\ is very close to those of the Sun ($\Delta T_\mathrm{eff} \approx XX$,
$\delta\logg \approx XX$, and $\Delta\feh \approx 0$),
we may approximate the pre-accretion abundances of \bizarreone\ with the Sun.
The expected $\Delta\elemH{X}$
in a Sun-like star's atmosphere by adding certain mass of bulk Earth composition
under these simplifying assumptions:
\begin{itemize}
  \item The material added is instantly and completely mixed.
  \item The atmospheric composition that we measure is identical throughout
    the star's radiative and convective zone.
  \item The surface abundance of the star has been altered only by the
    accretion event(s).
\end{itemize}
We take the solar abundances, $\elemH{X}$, of element \elem{X}
(\cite{Asplund:2009aa}) which can be converted to mass fraction as
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in e.g., atomic mass unit.
Assuming that the added material has a total mass $M_\mathrm{add}$, and the
mass fraction in each element $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
We take the composition of bulk Earth from a chondritic model of the Earth
(\cite{mcdonough2001composition}).
Similar calculations have been performed by \citet{Chambers:2010aa} and
\citet{Mack:2014aa,Mack:2016aa}.
